---
title: "Fem Def Cleaning"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
---

Female Defendents Cleaning Sheet 


#Step 1 - Read in Data, make sure to change wd to yours 

#all inquiries for data access can be directed to sarahsowell1@icloud.com

#Create Numeric and Charater value of Clean Typology
```{r}

femDef <- read.csv("Final Female Defendants - FEMALE DEFENDANTS.csv")
case <- read.csv("htd-normalized-cases_2024-06-14-16-06-02.csv")

#Rename Variable
femDef$typology <- femDef$FD.typology..CEO..Partner...Bottom..Manager..Associate...Victim...None..NEI

#Clean two cases of unclear coding
femDef$typology <- ifelse(femDef$typology == "NEI/ Victim", "NEI", femDef$typology)


femDef$typology <- ifelse(femDef$typology == "", "NEI", femDef$typology)

table(femDef$typology)

#Clean Text entries, double checking for mistyping. This creates a numeric and charater value
##Typoloy clean -> numeric :: Typoloy name :: charater



femDef$typologyClean <- ifelse(femDef$typology == "Victim",0, -999)

femDef$typologyClean <- ifelse(femDef$typology == "NEI/ Victim ", -999,femDef$typologyClean )

femDef$typologyName <- ifelse(femDef$typology == "Victim", "1. Victim", NA)

femDef$typologyClean <- ifelse(femDef$typology == "Manager",1, femDef$typologyClean)

femDef$typologyName <- ifelse(femDef$typology == "Manager", "1. Manager", femDef$typologyName)

femDef$typologyClean <- ifelse(femDef$typology == "Bottom",2, femDef$typologyClean)

femDef$typologyName <- ifelse(femDef$typology == "Bottom", "2. Bottom", femDef$typologyName)

femDef$typologyClean <- ifelse(femDef$typology == "Associate",3, femDef$typologyClean)

femDef$typologyName <- ifelse(femDef$typology == "Associate", "3. Associate", femDef$typologyName)

femDef$typologyClean <- ifelse(femDef$typology == "Partner",4, femDef$typologyClean)

femDef$typologyName <- ifelse(femDef$typology == "Partner", "4. Partner", femDef$typologyName)


femDef$typologyClean <- ifelse(femDef$typology == "NEI",-999, femDef$typologyClean)


femDef$typologyClean <- ifelse(femDef$typology == "Other",-888, femDef$typologyClean)


femDef$typologyClean <- ifelse(femDef$typology == "None",-888, femDef$typologyClean)


femDef$typologyClean <- ifelse(femDef$typology == "CEO",5, femDef$typologyClean)

femDef$typologyName <- ifelse(femDef$typology == "CEO", "5. CEO", femDef$typologyName)


table(femDef$typologyClean)
table(femDef$typologyName)
```



Clean Race Variable, grouping Native American and Indian into Other & Create Race Name 
```{r}

femDef$raceNew <- ifelse(femDef$race == "Native American", "Other", femDef$race)

femDef$raceNew <- ifelse(femDef$race == "Indian", "Other", femDef$raceNew)

femDef$raceNew <- ifelse(femDef$race == "", "Unknown", femDef$raceNew)

table(femDef$raceNew)

femDef$raceName <- ifelse(femDef$race=="White","1. White", femDef$race)
femDef$raceName <- ifelse(femDef$race=="Asian","2. Asian", femDef$raceName)
femDef$raceName <- ifelse(femDef$race=="Hispanic","3. Hispanic", femDef$raceName)
femDef$raceName <- ifelse(femDef$race=="Black","4. Black", femDef$raceName)
femDef$raceName <- ifelse(femDef$race=="Unknown","6. Unknown", femDef$raceName)
femDef$raceName <- ifelse(femDef$race=="Other","5. Other", femDef$raceName)


```


#Create a secondary, simplified Race Variable for modeling
```{r}

femDef$raceNew1 <- ifelse(femDef$raceNew == 'Asian', 'Other', femDef$raceNew)

femDef$raceNew1 <- ifelse(femDef$raceNew == 'Hispanic', 'Other', femDef$raceNew1)

femDef$raceNew1 <- ifelse(femDef$raceNew == 'Unknown', NA, femDef$raceNew1)

```


Create a dummy variable of if a person is a victim or victim-offender
```{r}

femDef$victimDummy <- ifelse(femDef$typologyClean >= 3, 1, 0)
femDef$victimDummyName <- ifelse(femDef$typologyClean >= 3, "Victim", "Not Victim")
table(femDef$victimDummyName)

```

Clean Age and Year Variable
```{r}
##Age
femDef$arrest_age <- ifelse(femDef$arrest_age >= 18, femDef$arrest_age, NA)
table(femDef$arrest_age)

##Year
femDef$year <- format(as.Date(femDef$charge_date, format="%Y-%m-%d"),"%Y")
table(femDef$year)
```



Combined Defendent Level Data with Case Level Data 
```{r}

library(dplyr)
femDefmerge <- femDef
table(femDef$case_id)

femDefmerge$case_id <- as.integer(femDef$Case_id)
case$case_id <- as.integer(case$case_id)

merge <- left_join(
  femDefmerge,
  case,
  by = "case_id",
  copy = TRUE, 
  suffix = c(".x", ".y"),
  multiple = "all"
)


names(merge)

```

#Create Binary Variable of Crimes Including a Minor
```{r}

femDef <- data.frame(merge)

table(femDef$minor_sex)

femDef$minor_catagorical <- ifelse(femDef$minor_sex == 'true', 1, 0)

femDef$minor_catagorical <- ifelse(femDef$minor_sex == 'true' & femDef$adult_sex == 'true', 2, femDef$minor_catagorical)

table(femDef$minor_catagorical)
```

#Create a Catagorical Variable of Minor Trafficking
```{r}



femDef$minorNice <- ifelse(femDef$minor_catagorical == 2, "Adult Victims Only", femDef$minor_catagorical)


femDef$minorNice <- ifelse(femDef$minor_catagorical == 1, "Adult & Minor Victims", femDef$minorNice)


femDef$minorNice <- ifelse(femDef$minor_catagorical == 0, "Minor Victims Only", femDef$minorNice)

class(femDef)


```


#Use regular expression to create binary variables of control methods
```{r}
library(stringr)




##Create Binary Variables for All Method of Control
femDef$control <- femDef$Method.of.Control...Caretaking...Verbal.threats...Physical.violence...Drugs.Alcohol...Withhold.something.of.value...Isolation....N.A....Other...Unknown

femDef$caretaking_binary <- as.integer(str_detect(femDef$control, regex("caretaking", ignore_case =  TRUE)))
table(femDef$caretaking_binary)

femDef$verb_binary <- as.integer(str_detect(femDef$control, regex("Verbal[:blank:]Threats", ignore_case =  TRUE)))
table(femDef$verb_binary)

femDef$physV_binary <- as.integer(str_detect(femDef$control, regex("Physical[:blank:]Violence", ignore_case =  TRUE)))
table(femDef$physV_binary)

femDef$drugs_binary<- as.integer(str_detect(femDef$control, regex("Drugs/Alcohol", ignore_case =  TRUE)))
table(femDef$drugs_binary)

femDef$witholdVal_binary<- as.integer(str_detect(femDef$control, regex("withhold[:blank:]something", ignore_case =  TRUE)))
table(femDef$witholdVal_binary)

femDef$isolation_binary<- as.integer(str_detect(femDef$control, regex("isolation", ignore_case =  TRUE)))
table(femDef$isolation_binary)


##Create Binary Variables of Administrator

femDef$admin <- femDef$Administration...Recruit...Train...Organize.buyer.engagements...Enforce...Handle.money..inc..posting.bonds....Personal.care..shopping..hair..etc.

femDef$recruit_binary <- as.integer(str_detect(femDef$admin, regex("recruit", ignore_case= TRUE)))
table(femDef$recruit_binary)

femDef$train_binary <- as.integer(str_detect(femDef$admin, regex("train", ignore_case= TRUE)))
table(femDef$train_binary)

femDef$organize_binary <- as.integer(str_detect(femDef$admin, regex("organize[:blank:]buyer", ignore_case= TRUE)))
table(femDef$organize_binary)

femDef$enforce_binary <- as.integer(str_detect(femDef$admin, regex("enforce", ignore_case= TRUE)))
table(femDef$train_binary)

femDef$money_binary <- as.integer(str_detect(femDef$admin, regex("handle[:blank:]money", ignore_case= TRUE)))
table(femDef$money_binary)

femDef$care_binary <- as.integer(str_detect(femDef$admin, regex("personal[:blank:]care", ignore_case= TRUE)))
table(femDef$care_binary)


#Create Binary Variable of Trafficker

femDef$trafficker <- ifelse(femDef$Trafficker.Yes.No.Unknown == 'Unknown', NA, 0)

femDef$trafficker <- ifelse(femDef$Trafficker.Yes.No.Unknown == 'Yes', 1, femDef$trafficker)

table(femDef$trafficker)

#Create Binary Variable of Prostitution

femDef$prostitution <- ifelse(femDef$Prostitution.Yes.No..Unknown == 'Unknown', NA, 0)

femDef$prostitution <- ifelse(femDef$Prostitution.Yes.No..Unknown == 'Yes', 1, femDef$prostitution)

table(femDef$prostitution)

#Create Binary of Family Relationships
femDef$Relationship.to.victims..Not.Family.Family <-  str_replace(femDef$Relationship.to.victims..Not.Family.Family, regex("not family", ignore_case = TRUE), "not")

femDef$family_binary <- as.integer(str_detect(femDef$Relationship.to.victims..Not.Family.Family, regex("family", ignore_case= TRUE)))

table(femDef$family_binary)

```

#Clean Up Sex by Assigning Names and Grouping Smaller Catagories
```{r}

table(femDef$type_of_sex)

femDef$type_of_sex1 <- ifelse(femDef$type_of_sex == "Other", "Other",femDef$type_of_sex)

femDef$type_of_sex1 <- ifelse(femDef$type_of_sex == "Bars & Cantinas", "Other",femDef$type_of_sex1)

femDef$type_of_sex1 <- ifelse(femDef$type_of_sex == "Escort Services", "Other",femDef$type_of_sex1)

femDef$type_of_sex1 <- ifelse(femDef$type_of_sex == "Pornography", "Other",femDef$type_of_sex1)

femDef$type_of_sex1 <- ifelse(femDef$type_of_sex == "Unknown", NA ,femDef$type_of_sex1)

femDef$type_of_sex1 <- ifelse(femDef$type_of_sex == "", NA ,femDef$type_of_sex1)

femDef$type_of_sex1 <- ifelse(femDef$type_of_sex == "Personal Sexual Servitude", "Other" ,femDef$type_of_sex1)

femDef$type_of_sex1 <- ifelse(femDef$type_of_sex == "Illicit Massage Business", "Other" ,femDef$type_of_sex1)

femDef$type_of_sex1 <- ifelse(femDef$type_of_sex == "Strip Club", "Other" ,femDef$type_of_sex1)

table(femDef$type_of_sex1)


```


##Create Dummy Variables for Trafficking Type
```{r}

femDef$online_dummy <- ifelse(femDef$type_of_sex == "Online Solicitation", "Online Solicitation","Other")
table(femDef$online_dummy)

femDef$outdoor_dummy <- ifelse(femDef$type_of_sex == "Outdoor Solicitation", "Outdoor Solicitation","Other")
table(femDef$outdoor_dummy)

femDef$brothel_dummy <- ifelse(femDef$type_of_sex == "Brothel", "Brothel","Other")
table(femDef$brothel_dummy)

```


```{r}
##Create Forgien National Variable


femDef$forgNat <- ifelse(femDef$number_victims_foreign > 0, 1, 0)

```

#Create Catagorical Age Groupings
```{r}

categorize_age <- function(age) {
  if (!is.na(age)) {
    if (age >= 18 & age <= 23) {
      group <- "18-23"
    } else if (age >= 24 & age <= 29) {
      group <- "24-29"
    } else if (age >= 30 & age <= 34) {
      group <- "30-34"
    } else if (age >= 35 & age <= 39) {
      group <- "35-39"
    } else {
      group <- "40+"
    }
    return(group)
  } else {
    return(NA)  # If age is missing, return NA
  }
}

# Add age group variable to femDef dataset
ageCount <- femDef %>%
  mutate(ageGroup = sapply(arrest_age, categorize_age))

table(ageCount$ageGroup)
```



#Download Clean Data
```{r}
#Remove blank rows
femDef1 <- subset(femDef, !is.na(femDef$Case_id))

#Remove Victim Catagory
femDef1 <- subset(femDef, (femDef$typologyName != "1. Victim"))
view(femDef1)
femDefClean <- write.csv(femDef1, "femDefClean5.csv")

```

